Project Protocol

### 2019-10-14 protocol.Rmd
Create the line up plots, normal errors

Each participant will first see three test displays, they will then undertake an online survey linked to them through the online crowdsource platform Figure-Eight.
Within the experiment:
A line up protocol will be used to arrange 20 maps into one display. Each display will be created by a combination of plot type, error distribution and spatial dependence, the possible levels of the factors are:
- Plot type: Geography, Hexagons
- Error distribution: Normal, Chi-Square
- Spatial Dependence: Rurality level, North to South, East to West
Allowing each factor combination to be considered will provide 12 (2*2*3) line up displays to be seen by all participants.
The order of these displays will be randomised for each participant. ??

>>>>

Each participant will first see three test displays, they will then undertake an online survey linked to them through the online crowdsource platform Figure-Eight.
Within the experiment:
A line up protocol will be used to arrange 20 maps into one display. Each display will be created by a combination of plot type, error distribution and spatial dependence, the possible levels of the factors are:
- Plot type: Geography, Hexagons
- Error distribution: Normal, Chi-Square
- Spatial Dependence: Rurality level, North to South, East to West
Allowing each factor combination to be considered will provide 12 (2x2x3) line up displays to be seen by all participants.
The order of these displays will be randomised for each participant. ??
